
\section{Skills}

\outerlist{

\entrybig
{\textbf{Information Technology}}{}
{Bash, Git, TCP/IP}{}
\innerlist{
	\entry{I would like to highlight the three that are most important to me. With access to git, bash, and TCP/IP it is possible to get anything done. Bash comes with its collection of built-in/scripting tools, not to mention the ability to write and compile code. Git, most known for its collaborative aspects, in the individual context allows for introspection, experimentation, and most importantly documentation over the course of a project. Finally, TCP/IP strings it all together, whether with FTP or the newest, shiniest API. There is no data set that can withstand the right tools and a systematic approach.}
	\entry{Here are the tech stacks I feel comfortable developing with:
	}
\entryextra{Full-stack (sans data layer) Web Applications: .NET with Razor Pages, Java with Spring, Python with Django or Flask}
\entryextra{Data Layer: MySQL, MSSQL, MongoDB}
\entryextra{Single Page Application Frameworks (Front End): Vue.js, JQuery/Bootstrap}
\entryextra{Web APIs: .NET, Java, Python, C/C++}
}

\entrybig
{\textbf{Languages}}{}
{English, German, French}{}
\innerlist{
	\entry{I am a native English speaker. The Goethe Institute has certified my German at the C2 level. I also did my undergraduate work in German, and have been speaking German in the workplace for the past six years. My incomparable wife and I have spoken German together for five of those. I could survive in Lyon with my French.}
}

}
