\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {2022 - Current}
		{Software Engineer}
		{Wonderz GmbH}
		{
      Oversaw engineering and architecture for growth-oriented features, accelerating business client onboarding.

        
      \vspace{10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Implemented web app for efficient bulk import of client multimedia content.
            \item Led OKR planning, MVP alignment, and provided strategic product direction.
            \item Developed and presented grant proposals, conducted stakeholder presentations.
            \item Contributed to developer education initiatives.
        \end{itemize}
        }\\
	\entry
		{2021 - 2022}
		{Software Engineer}
		{Cozero GmbH}
		{
Played a key role rewriting and scaling functionality to move the software beyond the MVP stage.
Transformed and established the engineering culture to empower, energize, and accelerate the
development of revolutionary carbon accounting.
      \vspace{10pt}

        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
          \item Created an xlsx and csv parser for bulk importing company carbon emissions data.
          \item Rewrote the carbon accounting module with a focus on scalability, performance, and modularity to ensure compliance with global carbon accounting frameworks.
          \item Successfully migrated the project from MongoDB to Postgres.
          \item Contributed to recruiting and talent retention efforts.
        \end{itemize} 
        }\\
	\entry
		{2019 - 2021}
		{Software Engineer}
		{ICS GmbH}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
        \item Collaborated with cross-functional teams to analyze workflows and implement efficient solutions, resulting in significant time and resource savings.
          \item    Engaged in full-stack development for a consumer-facing web app focused on order tracking.
          \item    Integrated with the company's order and inventory management APIs, alongside in-house customer journey software.
          \item    Implemented real-time package tracking using websockets for a handheld scanner.
        \end{itemize} 
        }\\
	\entry
		{2015 - 2019}
		{Assistant Project Manager}
		{AIFS}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
          \item  Championed process improvement through the automation of manual bureaucratic processes.
            \item Utilized project management skills to plan, execute, and monitor automation projects, ensuring seamless integration with existing systems.
            \item Worked closely with stakeholders to understand requirements, mitigate challenges, and deliver solutions that enhanced overall operational efficiency.
            \item Played a pivotal role in fostering a culture of continuous improvement and innovation within the organization.
        \end{itemize} 
        }
\end{entrylist}
